Research Notes

### 2018-06-11 writups/notes.tex
update notes w/ TODO, results from P
stash chebyshev notes

There are thus three possible solutions to this:
\begin{itemize}
    \item Consider BCs only on $P$, the only other choice of dynamical variable.

    \item Consider using a $\nabla^2 P$ equation instead of a $\vec{\nabla}
        \cdot \vec{u} = 0$ constraint. The correct choice of BCs in this case is
        discussed in Nordstrom et al, 2006.

@@

@@

>>>>

There are thus three possible solutions to this:
\begin{itemize}
    \item Consider BCs only on $P$, the only other choice of dynamical variable.
        This seems to also exhibit instabilities near $z = 0$.

    \item Consider using a $\nabla^2 P$ equation instead of a $\vec{\nabla}
        \cdot \vec{u} = 0$ constraint. The correct choice of BCs in this case is
        discussed in Nordstrom et al, 2006. We choose not to investigate this.

@@

TODO Can taking $\rho_1 \ll \rho_0$, giving us a full rank operator w/o doing
the janky double add thing, solve in the incompressible limit? Otherwise, go
anelastic.

@@

\chapter{Numerical Results}

\section{Chebyshev Polynomials}

Note that, unlike a Fourier basis, a Chebyshev basis has $N^2$ grid spacing near
its boundaries. By this, we mean that for the Chebyshev polynomials $T_n(x)$,
the spacing between zeros of $T_n(x)$ near $x = \pm 1$ scales like $n^{-2}$.
This contrasts with Fourier series for which $\psi_n(x) = \cos n\pi x, \sin n\pi
x$ for which the zeros are spaced $\Delta x = \frac{1}{n}$. This is important
because the CFL condition for PDEs requires that $u\frac{\Delta t}{\Delta x} <
C$ for some constant $C$, otherwise the simulation will move fluid elements more
than $\Delta x$ in a single timestep, an illegal operation for the basis
function.

If we consider instead $T_n(x)$ satisfying $T_n(\cos \theta) = \cos n\theta$,
then within some spacing of the edge of the domain $\cos\theta = 1 - \Delta x$
then $\Delta x \approx \theta^2/2$ then the number of zeros seen is the number
of solutions $\cos \phi = 0, \phi = n\theta = n\sqrt{2\Delta x}$ which requires
$\sim k\pi \in [0, n\sqrt{2\Delta x}]$. Thus, for any interval $\Delta x$, the
number of zeros contained scales with $n^2$!
